A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-02-10 analysis/article.Rmd
chore: remove comments

```{r ml, include = FALSE}
n_lrns <- sum(!grepl("^scale..*", bmrk_results$learners$learner_id))
#n_cv <- c(inner.folds
#    outer = unlist(
#        bmrk_results$resamplings$resampling[[1]]$param_set$get_values()
#    )
#)
```

>>>>

```{r ml, include = FALSE}
n_lrns <- sum(!grepl("^scale..*", bmrk_results$learners$learner_id))
```
